Describing the C-Space of Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-07-29 dit-paper_ieee.tex
- cspace size ratio computation and text

>>>>

\section{Experimental C-space size gain of asynchronous systems}
	One of the advantages of asynchronous systems over synchronous systems in the
	context of periodic tasks is that the critical instants of asynchronous systems
	cannot be more constraining for the C-space than synchronous instants. For this
	reason, it has long been known that modifying task offsets when possible during
	the design of a real-time system is a useful trick to fit a heavy but periodic task set
	into a given platform.

	In Fig.~\ref{fig:sizeRatio} a number of feasible asynchronous task sets without
	synchronous instants were generated and the size of their C-space was
	calculated and compared with the size of the C-space of the same
	task sets with all task offsets set to zero. In other words, this figure
	evaluates the feasibility gain of adding random offsets to a synchronous task
	set. It is assumed that a more advanced strategy to assign these offsets
	would yield a greater difference.

	\begin{figure}[h]
		\begin{center}
			\includegraphics[width=0.5\textwidth]{figs/sizeRatio.png}
			\caption{C-space size ratio between asynchronous and equivalent synchronous
			systems}
			\label{fig:sizeRatio}
		\end{center}
	\end{figure}
